Advanced Reactor Fuel Cycles Molten Salt Reactor Design

### 2016-10-20 MSR-design.tex
Determine interpolation bounds and reference temps for fuel and moderator.

As mentioned in \cref{sec:reactor}, the fuel salt enters the reactor at 1175
\textdegree F and leaves at 1225 \textdegree F. In order to cool the fuel salt
back down to its reactor inlet temperature, the coolant salt flows through the
heat exchanger at 850 \gls{gpm} with inlet and outlet temperatures of 1025
\textdegree F and 1100 \textdegree F respectively \cite{robertson_msre_1965}.

>>>>

As mentioned in \cref{sec:reactor}, the fuel salt enters the reactor at 1175
\textdegree F and leaves at 1225 \textdegree F. In order to cool the fuel salt
back down to its reactor inlet temperature, the coolant salt flows through the
heat exchanger at 850 \gls{gpm} with inlet and outlet temperatures of 1025
\textdegree F and 1100 \textdegree F respectively \cite{robertson_msre_1965}. A
summary of some of the important operating temperatures in the \gls{MSRE} is
given in \cref{tab:important_temps}.

\begin{table}[htpb]
    \begin{center}
      \begin{tabular}{l|c|c}
        Material \& Location & Temp (\textdegree F) & Temp (K) \\
        \hline \hline
        Fuel salt reactor inlet/heatx outlet         & 1175 & 908  \\
        Fuel salt reactor average outlet/heatx inlet & 1225 & 936  \\
        Fuel salt reactor max outlet                 & 1260 & 955  \\
        Coolant salt heatx inlet                     & 1025 & 825  \\
        Coolant salt heatx outlet                    & 1100 & 866  \\
        FLiBe boiling point                          & 2606 & 1703 \\
        Graphite core average                        & 1255 & 953  \\
        Graphite core maximum                        & 1300 & 978  \\
      \end{tabular}
    \end{center}
    \caption{Some important operating temperatures in the \gls{MSRE}}
    \label{tab:important_temps}
\end{table}

Based on the operating temperatures in \cref{tab:important_temps}, initial
interpolation tables will range from 824 to 1055 K for the fuel salt
temperature, and from 858 to 1088 K for the moderator temperature. The minimum
fuel salt temperature is equal to the heat exchanger inlet coolant salt
temperature, while the maximum fuel salt temperature is 100 K greater than the
maximum fuel salt core outlet temperature. The moderator limits are 60
\textdegree F greater than their fuel counterparts based on the experimental
observation by Robertson that moderator temperatures are only ever about 60
\textdegree F above the adjacent fuel. Reference temperatures for the fuel and
moderator will be 922 K (the average of reactor inlet and outlet temperatures)
and 953 K (graphite core average) respectively. These simulation set-points are
summarized in \cref{tab:sim_temps}.

\begin{table}[htpb]
    \begin{center}
      \begin{tabular}{l|c}
        Serpent Simulation Temperatures & Value (K)\\
        \hline \hline
        Fuel minimum        & 824 \\
        Fuel maximum        & 1055 \\
        Fuel reference      & 922 \\
        Moderator minimum   & 858 \\
        Moderator maximum   & 1088 \\
        Moderator reference & 953 \\
      \end{tabular}
    \end{center}
    \caption{Relevant temperature parameters for Serpent simulations}
    \label{tab:sim_temps}
\end{table}
